\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym} % additional symbols for technical documents
\usepackage[empty]{fullpage}
\usepackage{titlesec} % custom format of section titles
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem} % custom list environments
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr} % custom headers and footers
\usepackage[english]{babel} % multilingual support
\usepackage{tabularx} 
\usepackage{mathptmx} % decfault font used: Times New Roman
\usepackage{setspace}
\input{glyphtounicode} % PDF output to ensure proper mapping of glyphs to Unicode characters
% \linespread{0.8}
\setstretch{0.95}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% fancy
\pagestyle{fancy}
\fancyhf{} % clear header and footer fields
\fancyfoot{}
\setlength{\footskip}{1cm}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
% \addtolength{\textheight}{0in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ==============================

% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1}
  }
}

\newcommand{\resumeItemThin}[1]{
  \item{
    {#1 \vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{0.985\textwidth}[t]{l@{\extracolsep{\fill}}r@{\hspace{-0.1in}}}
        {\textbf{#1}} & {#2} \\
        #3 &  #4 \\
    \end{tabular*}\vspace{-5pt}
}

\titlespacing{\section}{0pt}{17pt}{13pt}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.00in, rightmargin=-0.2in, label={}]\vspace{3pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-10pt}}
\newcommand{\resumeItemListStart}{\vspace{3pt}\begin{itemize}[leftmargin=0.15in, rightmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ==============================

\begin{document}

% -----------HEADING-----------

\begin{center}
  \textbf{\Huge \scshape {Juhun Park}} \\ \vspace{3pt}
  % No sponsorship needed, F1 OPT \\
   202-924-4546 $|$
  \href{mailto:juhunpark32@gmail.com}{juhunpark32@gmail.com} $|$
  \href{https://www.juhunpark.me/}{juhunpark.me} $|$
  \href{https://linkedin.com/in/juhun-park}{linkedin.com/in/juhun-park} $|$
  \href{https://github.com/juhun32}{github.com/juhun32} \\
\end{center}

\vspace{-10pt}

% -----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{George Mason University}{Expected May 2027}
{Bachelor of Science in Computer Science}{GPA: 3.9}
\resumeItem{\textbf{Relevant Coursework: } Data Structures \& Algorithms, Low-level Programming} \\
{\textbf{Honors: }{\$20,000 Merit Scholarship Recipient}}
\resumeSubHeadingListEnd

% -----------WORK EXPERIENCE-----------

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Google Developer Groups} {Jul 2025 - Present}
{Technical Lead, George Mason University} {Remote}
\resumeItemListStart
\resumeItem{Developing a scalable Next.js dashboard that manages event details and meeting schedules.}
\resumeItem{Leading a community of 50+ developers; running Agile sprints with GitHub to deliver 2 full-stack products for GMU.}
\resumeItemListEnd

\resumeSubheading
{Northwestern University} {Jul 2025 - Aug 2025}
{Software Engineer Intern} {Remote}
\resumeItemListStart
\resumeItem{Launched a ASP.NET Minimal API \& SvelteKit MVP, serving 1500 users with 99.9\% uptime on Cloudflare.}
\resumeItem{Designed PostgreSQL schema and SQL functions on Supabase, with performant query execution time of sub-5ms.}
\resumeItem{Implemented CDN + Redis caching and REST endpoints, offloading 95\% of reads and cutting latency to sub-150ms.}
\resumeItemListEnd

\resumeSubheading
{George Mason University} {Sep 2024 - Dec 2024}
{Software Engineer Intern} {Remote}
\resumeItemListStart
\resumeItem{Implemented JWT Google OAuth, refactored Django service into modular apps, improving API throughput by 30\%.}
\resumeItem{Wrote unit tests with Pytest, increasing CRUD API test coverage from 20\% to 85\%, caught 2 critical issues pre-launch.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% -----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart

\resumeSubheading
{Copium.dev} {Jan 2025 - Jun 2025}
{Co-Founder} {Remote}
\resumeItemListStart
\resumeItem{Merger with Cvrve (2025), launched a tech career management platform serving 400k users, 90k job applications daily.}
\resumeItem{Deployed 10k+ events/s analytics pipeline (Kafka to ClickHouse, Redis) in Go as Docker containers on AWS ECS.}
\resumeItem{Set up an object storage pipeline using Cloudflare R2, offloading 57GB/month from S3 and eliminating egress costs.}
\resumeItem{Automated builds and deployments with Terraform + GitHub Actions, achieving sub-10min deployment times.}
\resumeItemListEnd

\resumeSubheading
{\textbf{Formulaba} \textnormal{$|$ \href{https://github.com/juhun32/ldfd}{GitHub}}} {2025}
{{Next.js, Node.js}}{Landsdowne Family Dentistry, Alexandria, VA}
\resumeItemListStart
\resumeItem{Redesigned a local dental office website with Next.js, improved Lighthouse performance score from 75 to 95.}
\resumeItem{Improved compared to previous, FCP 1.9s to 0.9s, LCP 6.4s to 2.2s, TBT 130ms to 30ms, Speed Index 2.7s to 0.9s.}
\resumeItemListEnd

\resumeSubheading
{\textbf{Californian Temple} \textnormal{$|$ \href{https://github.com/juhun32/calple}{GitHub} $|$ \href{https://www.calple.date}{calple.date}}} {}
{{Go, Next.js, Firestore, Docker, GCP Cloud Run}}{}
\resumeItemListStart
\resumeItem{Built a collaborative relationship management app with shared calendars, cycle tracking, and real-time synced maps.}
\resumeItem{Exposed Golang REST APIs and deployed 30MB image to Cloud Run, sustaining 99.9\% uptime with autoscaling.}
\resumeItem{Optimized Firestore access patterns to keep API latency sub-150ms, handling 1k+ daily API requests.}
\resumeItemListEnd

\resumeSubheading
{\textbf{Sequantial} \textnormal{$|$ \href{https://github.com/juhun32/project-verstappen}{GitHub}}} {}
{{Python, Shared Memory API, OpenCV, AC/acsys module (Assetto Corsa Internal API)}}{}
\resumeItemListStart
\resumeItem{Architected a real-time Assetto Corsa telemetry pipeline, streamed events to Kafka for web based interactive analysis.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% -----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
\resumeItemThin{\textbf{Languages: }{Python, TypeScript, JavaScript, Go, Java, SQL, C, C\#}}\\
% \resumeItemThin{\textbf{Libraries \& Frameworks: }{React, SvelteKit, FastAPI, Django, Flask, .NET, PostgreSQL, Pytest}}\\
% \resumeItemThin{\textbf{Web \& APIs: } HTTP, HTML/DOM, CSS, AJAX, REST APIs, JSON, OAuth/OIDC}\\
\resumeItemThin{\textbf{Frameworks: } React, Node.js, Django, Flask, Next.js, SvelteKit, FastAPI, .NET, PostgreSQL}\\
\resumeItemThin{\textbf{Tools \& Platforms: }{Git, GCP, Vercel, Cloudflare, Pub/Sub, AWS, Linux, RabbitMQ, Algolia, Docker, Redis, Kafka}}\\
\resumeItemListEnd

\end{document}