\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym} % additional symbols for technical documents
\usepackage[empty]{fullpage}
\usepackage{titlesec} % custom format of section titles
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem} % custom list environments
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr} % custom headers and footers
\usepackage[english]{babel} % multilingual support
\usepackage{tabularx} 
\usepackage{mathptmx} % decfault font used: Times New Roman
\usepackage{setspace}
\input{glyphtounicode} % PDF output to ensure proper mapping of glyphs to Unicode characters
\setstretch{1}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% fancy
\pagestyle{fancy}
\fancyhf{} % clear header and footer fields
\fancyfoot{}
\setlength{\footskip}{1cm}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{.2in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-9pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ==============================

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeItemThin}[1]{
  \item\small{
    {#1 \vspace{-7pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r@{\hspace{-0.2in}}}
        \small{\textbf{#1}} & \small{#2} \\
        \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r@{\hspace{-0.2in}}}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r@{\hspace{-0.2in}}}
        \small#1 & \small#2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.00in, rightmargin=-0.2in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, rightmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

% ==============================

\begin{document}

% -----------HEADING-----------

\begin{center}
  \textbf{\Huge \scshape {Juhun Park}} \\ \vspace{1pt}
  \small 202-924-4546 $|$
  \href{mailto:riann3207@gmail.com}{\underline{juhunpark32@gmail.com}} $|$
  \href{https://juhun-park.web.app/}{\underline{juhun-park.web.app}} $|$
  \href{https://linkedin.com/in/juhun-park}{\underline{LinkedIn}} $|$
  \href{https://github.com/juhun32}{\underline{GitHub}} \\
\end{center}

\vspace{-7pt}

% -----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\vspace{3pt}
\resumeItemListStart
\resumeItemThin{\textbf{Programming Languages: } {Python, Java, SQL, HTML, CSS, JavaScript}}\\
\resumeItemThin{\textbf{Frameworks: }{React, Flask, Bootstrap, Django, Pandas, Numpy, PostgreSQL, MediaPipe}}\\
\resumeItemThin{\textbf{Technologies: } {Git, Linux, Anaconda3, VS Code, LaTeX, Eclipse, MS Office}}\\
\resumeItemListEnd
\vspace{3pt}

% -----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{George Mason University}{Fairfax, VA}
{BS Computer Science, ADVANCE Program}{Expected May 2027}\\

\resumeSubheading
{Northern Virginia Community College}{Annandale, VA}
{AS Computer Science, GPA: 3.9; Dean's List '23, '24; Presidential Scholar '24}{Expected May 2025} \\

\resumeItem{\textbf{Relevant Courses: }{Problem Solving\&Programming, Object Oriented Programming, Data Structures\&Algorithms, Calculus I/II/III}}
\resumeSubHeadingListEnd

% -----------WORK EXPERIENCE-----------

% \section{Experience}
%     \resumeSubHeadingListStart

%         \resumeSubheading
%             {Undergraduate Research Assistant}{June 2020 -- Present}
%             {Texas A\&M University}{College Station, TX}
%         \resumeItemListStart
%             \resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems}
%             \resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data}
%             \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
%         \resumeItemListEnd

%         \resumeSubheading
%             {Information Technology Support Specialist}{Sep. 2018 -- Present}
%             {Southwestern University}{Georgetown, TX}
%         \resumeItemListStart
%             \resumeItem{Communicate with managers to set up campus computers used on campus}
%             \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
%             \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
%         \resumeItemListEnd

%         \resumeSubheading
%             {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
%             {Southwestern University}{Georgetown, TX}
%         \resumeItemListStart
%             \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
%             \resumeItem{Developed a game in Java to test the generated dungeons}
%             \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
%             \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
%             \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
%             \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
%         \resumeItemListEnd

\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading
{Eduverse}{December 2024 -- Present}
{Backend Developer}{Remote}
\resumeItemListStart
\resumeItem{Implemented an ML-based recommendation algorithm using \textbf{Python} and \textbf{Django} suggesting user connections, personalized posts.}
\resumeItem{Developed search endpoint using \textbf{Django ORM}, \textbf{PostgreSQL} to query profiles and posts with filters for names, skills, post types.}
% \resumeItem{Designed and integrated post management features including comments, likes, saves, shares, and favorites.}
\resumeItem{Collaborated on API testing, debugging using \textbf{Postman} and \textbf{Git}, ensuring profile post-related functionality achieved \textbf{98\% accuracy}.}
\resumeItem{Implemented backend features, search features with seamless \textbf{React} integration for frontend functionality, deployed using \textbf{Firebase}.}
\resumeItem{Worked as a team of 6 to develop and deploy scalable backend services, ensuring high availability and performance.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{21Cen. English \& Math Academy}{July 2024 -- August 2024}
{English Instructor}{Incheon, South Korea}
\resumeItemListStart
\resumeItem{Improved 14 high school students' grades by average 30\%, significantly improved understanding of English concepts and structures.}
\resumeItem{Saved 20\% of class time by developing 10 custom lesson plans, addressing the specific needs and objectives of all 14 students.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Himedia Academy}{January 2023 -- April 2023}
{Full-stack Developer Apprenticeship}{Seoul, South Korea}
\resumeItemListStart
\resumeItem{Full-time development training consisted of 10 apprentices, on \textbf{Java}, \textbf{Python} backend application and practical workspace training.}
\resumeItem{Developed foundational skills in web development techniques using \textbf{Bootstrap}, \textbf{HTML/CSS}, \textbf{JavaScript}, and \textbf{Oracle DBMS}.}
\resumeItem{Focused on backend development skills; object-oriented programming, data structures and algorithms, unit testing, and debugging.}
\resumeItem{Led a team of 4 and improved workflow efficiency by reducing \textbf{30\%} of development time by utilizing \textbf{Git}, \textbf{Github} and \textbf{Notion}.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Science Research Program, Gimpo Highschool}{March 2021 -- November 2021}
{Student Researcher}{Gimpo, South Korea}
\resumeItemListStart
\resumeItem{Led a research project, developed and tested a motion detection application using \textbf{Numpy}, \textbf{OpenCV}, \textbf{PyAutoGUI} and \textbf{MediaPipe}.}
\resumeItem{Authored a scientific research paper detailing the project methodology, test results, and implications for future research plans.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% -----------PROJECTS-----------

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Project Verstappen} $|$ \href{https://github.com/juhun32/project-verstappen}{\underline{GitHub}} $|$ Python, Shared Memory API, OpenCV, AC/acsys module}{2025}
\resumeItemListStart
\resumeItem{Integrated the \textbf{Assetto Corsa Shared Memory API} and \textbf{AC/acsys module} for real-time session telemetry, vehicle data for analysis.}
\resumeItem{Utilized preprocessing pipelines using \textbf{OpenCV} to extract track lines for lane detection.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Formula One Statistics} $|$ \href{https://github.com/juhun32/f1-statistics}{\underline{GitHub}} $|$ Flask, React, PostgreSQL, OpenF1 API, Firebase, Docker, Google Cloud Run}{2025}
\resumeItemListStart
\resumeItem{Designed a comprehensive database schema using \textbf{Python} and \textbf{PostgreSQL} to store championship points allocations data.}
\resumeItem{Implemented backend API using \textbf{Flask} to fetch, filter, store, update data from OpenF1 API, with data tables and interactive graphs.}
\resumeItem{Developed frontend interface with \textbf{React} for users to navigate through updated driver/constructor standings and grand prix statistics.}
\resumeItemListEnd

% \resumeProjectHeading
% {\textbf{Web iOS Calculator} $|$ \href{https://github.com/juhun32/ios-calculator}{\underline{github.com/juhun32/ios-calculator}}}{2024}
% \resumeItemListStart
% \resumeItem{Utilized: HTML, CSS, JavaScript, Github Pages}
% \resumeItem{Developed a functional calculator that mimics iOS 13 calculator design and functionality, with 1:1 scale ratio and same functionality.}
% \resumeItemListEnd

\resumeSubHeadingListEnd

% -----------EXTRACURRICULAR ACTIVITIES-----------

\section{Extracurricular Activities}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Web Developer Volunteer, InsightLegi DataStorm '25} $|$ \href{https://github.com/juhun32/datastorm25}{\underline{GitHub}} $|$ React, Bootstrap, Firebase}{January 2025}
\resumeItemListStart
\resumeItem{Developed a static website using \textbf{React} and \textbf{Bootstrap} to promote Hackathon 2025, including event details and registration process.}
\resumeItem{Deployed the project on \textbf{Firebase Hosting}, enabling fast and scalable access.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{PatriotHacks '24} $|$ \href{https://github.com/juhun32/Prison-Break}{\underline{GitHub}} $|$ React, Github Pages}{October 2024}
\resumeItemListStart
\resumeItem{Participated in a 36-hour hackathon event, collaborated with 3 team members to develop a \textbf{React} web application that provides information about government spending of tax revenue on incarceration, and solutions to reduce spending on prison facilities.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{CodePath Technical Interview Prep Course} - \emph{TIP102}}{May 2024 -- August 2024}
\resumeItemListStart
\resumeItem{Improved problem-solving skills of data structures and algorithms of heaps, trees, linked lists, and hashmap through 60+ problems.}
\resumeItem{Enhanced communication and analytical thinking skills by collaborating with 5 team members from various cultural backgrounds.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{President of Software Developer Student Club}, Gimpo Highschool}{August 2020 -- March 2022}
\resumeItemListStart
\resumeItem{Led 40 club members, supported their projects and academic success, recieved 100\% positive feedback from members and mentors.}
\resumeItem{Organized two successful project demonstration event, coordinated logistics, presentations, and attendee engagement.}
\resumeItem{Invited a published author in AI for a Q\&A, facilitated understanding of AI concepts and inspired a new AI application project.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}