\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym} % additional symbols for technical documents
\usepackage[empty]{fullpage}
\usepackage{titlesec} % custom format of section titles
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem} % custom list environments
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr} % custom headers and footers
\usepackage[english]{babel} % multilingual support
\usepackage{tabularx} 
\usepackage{mathptmx} % decfault font used: Times New Roman
\usepackage{setspace}
\input{glyphtounicode} % PDF output to ensure proper mapping of glyphs to Unicode characters
% \linespread{0.8}
\setstretch{1}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% fancy
\pagestyle{fancy}
\fancyhf{} % clear header and footer fields
\fancyfoot{}
\setlength{\footskip}{1cm}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
% \addtolength{\textheight}{0in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ==============================

% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1}
  }
}

\newcommand{\resumeItemThin}[1]{
  \item{
    {#1 \vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{minipage}[t]{0.985\textwidth}
      \textbf{#1} \hfill #2 \\
      {#3} \hfill {#4}
    \end{minipage}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{minipage}[t]{0.985\textwidth}
      \textbf{#1} \hfill \\
      {#2}
    \end{minipage}\vspace{-5pt}
}

\titlespacing{\section}{0pt}{17pt}{13pt}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.00in, rightmargin=-0.2in, label={}]\vspace{3pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-10pt}}
\newcommand{\resumeItemListStart}{\vspace{3pt}\begin{itemize}[leftmargin=0.15in, rightmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ==============================

\begin{document}

% Header

\begin{center}
  \textbf{\Huge \scshape {Juhun Park}} \\ \vspace{3pt}
  % No sponsorship needed, F1 OPT \\
   202-924-4546 $|$
  \href{mailto:juhunpark32@gmail.com}{juhunpark32@gmail.com} $|$
  \href{https://www.juhunpark.me/}{juhunpark.me} $|$
  \href{https://linkedin.com/in/juhun-park}{linkedin.com/in/juhun-park} $|$
  \href{https://github.com/juhun32}{github.com/juhun32} \\
\end{center}

\vspace{-10pt}

% Education

\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{George Mason University}{Expected May 2027}
{Bachelor of Science in Computer Science}{GPA: 4.0}
\resumeItem{\textbf{Relevant Coursework: } Data Structures \& Algorithms, Low-level Programming} \\
{\textbf{Honors: }{\$20,000 Merit Scholarship Recipient}}
\resumeSubHeadingListEnd

% Work experience

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Google Developer Groups} {Aug 2025 - Present}
{Lead Developer, George Mason University} {Fairfax, VA}
\resumeItemListStart
\resumeItem{Architected a course scheduler with Go and PostgreSQL to ingest and manage 10,000+ university course sections.}
\resumeItem{Integrated backtracking algorithm to solve the constraint satisfaction problem, generating conflict-free timetables.}
\resumeItem{Engineered a data pipeline using Python and GitHub Actions to automatically scrape course catalog with 99.9\% accuracy.}
\resumeItem{Scaled with RabbitMQ and Redis for asynchronous processing, supporting 100+ concurrent users without degradation.}
\resumeItemListEnd

\resumeSubheading
{Northwestern University} {Jun 2025 - Aug 2025}
{Software Engineer Intern} {Evanston, IL}
\resumeItemListStart
\resumeItem{Built an alumni networking platform with SvelteKit and ASP.NET, serving 150 users with 99.9\% uptime on Cloudflare.}
\resumeItem{Engineered a PostgreSQL schema, optimized indexes, SQL functions on Supabase achieving p99 sub-5ms query latency.}
\resumeItem{Configured a multi-tier caching strategy using Cloudflare CDN and a Redis cache, offloading 95\% of read requests.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% Projects
\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{Copium.dev \textnormal{$|$ \href{https://github.com/juhun32/copium}{GitHub} $|$ \href{https://www.copium.dev}{copium.dev}}}
{{Go, TypeScript, SvelteKit, PostgreSQL, Algolia, GCP, AWS, Cloudflare}}
\resumeItemListStart
\resumeItem{Launched an internship management platform with SvelteKit and PostgreSQL, processing 2000+ weekly applications.}
% \resumeItem{Scaled real-time analytics pipeline to 1k+ events/s with Kafka and Go consumers on AWS ECS, feeding into ClickHouse.}
\resumeItem{Delivered an 80\% reduction in query latency for BigQuery analytics by leveraging CQRS architecture.}
\resumeItem{Migrated media storage to Cloudflare R2, architecting a zero-egress pipeline without incurring AWS data transfer fees.}
\resumeItem{Implemented fault-tolerant compensating transactions for consistency across 3 data stores with automated retries.}
\resumeItemListEnd

\resumeProjectHeading
{Californian Temple \textnormal{$|$ \href{https://github.com/juhun32/calple}{GitHub} $|$ \href{https://www.calple.date}{calple.date}}}
{{Go, Next.js, Firestore, Docker, GCP Cloud Run}}
\resumeItemListStart
\resumeItem{Designed an event pipeline using GCP Pub/Sub to ingest disparate streams into a unified Firestore state model.}
\resumeItem{Developed a Go microservice to consume event streams, merging data real-time to predict and identify schedule conflicts.}
\resumeItem{Achieved sub-100ms latency for event synchronization by optimizing Firestore listener patterns \& gRPC communication.}
\resumeItemListEnd

\resumeProjectHeading
{Sequantial \textnormal{$|$ \href{https://github.com/juhun32/project-verstappen}{GitHub}}}
{{Python, Kafka, gRPC, Docker, Git, AC/acsys (Assetto Corsa Internal API)}}
\resumeItemListStart
\resumeItem{Coded a data pipeline to ingest real-time telemetry from Assetto Corsa, interfacing directly with the Shared Memory API.}
\resumeItem{Architected a high-throughput telemetry pipeline using Kafka to decouple game loop ingestion from data processing.}
% \resumeItem{Utilized Kafka's consumer groups to ensure zero data loss during connection loss, for fault tolerance.}
\resumeItem{Leveraged Kafka's keyed partitioning to guarantee sequential ordering of events, ensuring accuracy despite network loss.}
\resumeItemListEnd

% \resumeSubheading
% {INITech - EPDM} {}
% {Next.js}{}
% \resumeItemListStart
% \resumeItem{ABC.}
% \resumeItemListEnd

\resumeSubHeadingListEnd

% -----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
\resumeItemThin{\textbf{Languages: }{Python, TypeScript, JavaScript, Go, Java, SQL, C, C\#}}\\
% \resumeItemThin{\textbf{Libraries \& Frameworks: }{React, SvelteKit, FastAPI, Django, Flask, .NET, PostgreSQL, Pytest}}\\
% \resumeItemThin{\textbf{Web \& APIs: } HTTP, HTML/DOM, CSS, AJAX, REST APIs, JSON, OAuth/OIDC}\\
\resumeItemThin{\textbf{Frameworks: } React, Node.js, Django, Flask, Next.js, SvelteKit, FastAPI, .NET, PostgreSQL}\\
\resumeItemThin{\textbf{Tools \& Platforms: }{Git, GCP, Vercel, Cloudflare, Pub/Sub, AWS, Linux, RabbitMQ, Docker, Redis, Kafka}}\\
\resumeItemListEnd

\end{document}