\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym} % additional symbols for technical documents
\usepackage[empty]{fullpage}
\usepackage{titlesec} % custom format of section titles
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem} % custom list environments
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr} % custom headers and footers
\usepackage[english]{babel} % multilingual support
\usepackage{tabularx} 
\usepackage{mathptmx} % decfault font used: Times New Roman
\usepackage{setspace}
\input{glyphtounicode} % PDF output to ensure proper mapping of glyphs to Unicode characters
\setstretch{1}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% fancy
\pagestyle{fancy}
\fancyhf{} % clear header and footer fields
\fancyfoot{}
\setlength{\footskip}{1cm}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{.2in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-9pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ==============================

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeItemThin}[1]{
  \item\small{
    {#1 \vspace{-8pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r@{\hspace{-0.1in}}}
        \small{\textbf{#1}} & \small{#2} \\
        \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r@{\hspace{-0.1in}}}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r@{\hspace{-0.1in}}}
        \small#1 & \small#2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-9pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.00in, rightmargin=-0.2in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-9pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, rightmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-9pt}}

% ==============================

\begin{document}

% -----------HEADING-----------

\begin{center}
  \textbf{\Huge \scshape {Juhun Park}} \\ \vspace{1pt}
  \small 202-924-4546 $|$
  \href{mailto:riann3207@gmail.com}{\underline{juhunpark32@gmail.com}} $|$
  \href{https://juhun-park.web.app/}{\underline{juhun-park.web.app}} $|$
  \href{https://linkedin.com/in/juhun-park}{\underline{LinkedIn}} $|$
  \href{https://github.com/juhun32}{\underline{GitHub}} \\
\end{center}

\vspace{-7pt}

% -----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\vspace{3pt}
\resumeItemListStart
\resumeItemThin{\textbf{Programming Languages: }{Python, Java, SQL, JavaScript}}\\
\resumeItemThin{\textbf{Frameworks: }{React.js, Flask, Bootstrap, Django, Pandas, Numpy, PostgreSQL, MediaPipe, Tailwind}}\\
\resumeItemThin{\textbf{Technologies: }{Git, Linux, Docker, Firebase, GCP}}\\
\resumeItemListEnd
\vspace{3pt}

% -----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{George Mason University}{Fairfax, VA}
{BS Computer Science, ADVANCE Program}{Expected May 2027}\\

\resumeSubheading
{Northern Virginia Community College}{Annandale, VA}
{AS Computer Science, GPA: 3.9; Dean's List '23, '24; Presidential Scholar '24}{Expected May 2025} \\

\resumeItem{\textbf{Relevant Courses: }{Problem Solving \& Programming, Object Oriented Programming, Data Structures \& Algorithms, Calculus I/II/III}}
\resumeSubHeadingListEnd

% -----------WORK EXPERIENCE-----------

%         \resumeSubheading
%             {Undergraduate Research Assistant}{June 2020 -- Present}
%             {Texas A\&M University}{College Station, TX}
%         \resumeItemListStart
%             \resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems}
%             \resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data}
%             \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
%         \resumeItemListEnd

%         \resumeSubheading
%             {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
%             {Southwestern University}{Georgetown, TX}
%         \resumeItemListStart
%             \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
%             \resumeItem{Developed a game in Java to test the generated dungeons}
%             \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
%             \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
%             \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
%             \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
%         \resumeItemListEnd

\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading
{Eduverse} {December 2024 -- Present}
{Full-stack Developer Intern} {Remote}
\resumeItemListStart
\resumeItem{Implemented search, post features, optimized React integration efficiency by \textbf{50\%}, reducing search query response time by \textbf{20\%}.}
\resumeItem{Developed search endpoint using Django ORM, PostgreSQL to query profiles and posts with filters for names, skills, and post types.}
\resumeItem{Redesigned the frontend using React and Bootstrap, resulting in \textbf{50\%} reduction in page load time, \textbf{30\%} decrease in API fetch time.}
\resumeItem{Collaborated as a team of 5 on API testing using Postman and cURL, achieved \textbf{98\% accuracy} for profile and post-related features.}
% \resumeItem{Implemented an ML-based recommendation algorithm using Python and Django to suggest relevant user connections and posts.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Himedia Academy} {January 2023 -- April 2023}
{Full-stack Developer Apprenticeship} {Seoul, South Korea}
\resumeItemListStart
\resumeItem{Mastered core web development technologies and REST API development using HTML/CSS, JavaScript, Bootstrap, Oracle DBMS.}
\resumeItem{Acquired backend development skills of Object-oriented programming, data structures and algorithms, unit testing, debugging.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Science Research Program, Gimpo Highschool} {March 2021 -- November 2021}
{Student Researcher} {Gimpo, South Korea}
\resumeItemListStart
\resumeItem{Led a research project, developed and tested a motion detection application utilizing Numpy, OpenCV, PyAutoGUI, and MediaPipe.}
\resumeItem{Improved application accuracy of the motion-controlled pointer by \textbf{25\%} through optimization of MediaPipe and OpenCV code, resulting in a \textbf{20\%} performance enhancement.}
\resumeItem{Demonstrated strong research and communication skills, authored comprehensive scientific research paper documenting the project.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% -----------PROJECTS-----------

\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Project Verstappen} | \href{https://github.com/juhun32/project-verstappen}{\underline{GitHub}} | Python, Shared Memory API, OpenCV, AC/acsys module} {2024}
\resumeItemListStart
\resumeItem{Developed a real-time telemetry and data analysis system: Successfully integrated the Assetto Corsa Shared Memory API and AC/acsys module to extract real-time session telemetry and vehicle data for in-depth analysis.}
\resumeItem{Utilized OpenCV to develop, implement advanced image processing pipelines for accurate track line extraction and lane detection.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{FO Statistics} | \href{https://github.com/juhun32/f1-statistics}{\underline{GitHub}} | Flask, React, Tailwind CSS, OpenF1 API, FastF1 API, Firebase, Docker, GCP} {2024}
\resumeItemListStart
\resumeItem{Developed a robust backend API using Flask to fetch, filter data from the OpenF1 and FastF1 APIs, for \textbf{100+} data tables and graphs.}
\resumeItem{Created an intuitive and user-friendly interface: Designed and developed a highly interactive frontend using React and Tailwind CSS, providing users with seamless navigation through updated driver/constructor standings and comprehensive grand prix statistics.}
\resumeItem{Successfully deployed a production-ready backend API on Google Cloud Run utilizing Docker for containerization and leveraged Firebase for secure and efficient hosting of the React frontend.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% -----------EXTRACURRICULAR ACTIVITIES-----------

\section{Extracurricular Activities}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Web Developer Volunteer, InsightLegi DataStorm '25} $|$ \href{https://github.com/juhun32/datastorm25}{\underline{GitHub}} $|$ React, Bootstrap, Firebase}{January 2025}
\resumeItemListStart
\resumeItem{Developed a static website using \textbf{React} and \textbf{Bootstrap} to promote Hackathon 2025, including event details and registration process.}
% \resumeItem{Deployed the project on \textbf{Firebase Hosting}, enabling fast and scalable access.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{PatriotHacks '24} $|$ \href{https://github.com/juhun32/Prison-Break}{\underline{GitHub}} $|$ React, Github Pages}{October 2024}
\resumeItemListStart
\resumeItem{Participated in a 36-hour hackathon event, collaborated with 3 team members to develop a \textbf{React} web application that provides information about government spending of tax revenue on incarceration, and solutions to reduce spending on prison facilities.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{CodePath Technical Interview Prep Course} - \emph{TIP102} $|$ \href{https://drive.google.com/file/d/1AF2ZAUXoXeakbAZIJZ_izQ2nd9aNfjYB/view?usp=sharing}{\underline{Certificate}}}{May 2024 -- August 2024}
\resumeItemListStart
\resumeItem{Improved problem-solving skills of data structures and algorithms of heaps, trees, linked lists, and hashmap through \textbf{60+} problems.}
\resumeItem{Enhanced communication and analytical thinking skills by collaborating with \textbf{5 team members} from various cultural backgrounds.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% \resumeSubHeadingListStart
% \resumeProjectHeading
% {\textbf{President of Software Developer Student Club}, Gimpo Highschool}{August 2020 -- March 2022}
% \resumeItemListStart
% \resumeItem{Led \textbf{40} club members, supported their projects and academic success, recieved \textbf{100\%} positive feedback from members and mentors.}
% \resumeItem{Organized two successful project demonstration event, coordinated logistics, presentations, and attendee engagement.}
% \resumeItem{Invited a published author in AI for a Q\&A, facilitated understanding of AI concepts and inspired a new AI application project.}
% \resumeItemListEnd
% \resumeSubHeadingListEnd

\end{document}