\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym} % additional symbols for technical documents
\usepackage[empty]{fullpage}
\usepackage{titlesec} % custom format of section titles
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem} % custom list environments
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr} % custom headers and footers
\usepackage[english]{babel} % multilingual support
\usepackage{tabularx} 
\usepackage{mathptmx} % decfault font used: Times New Roman
\usepackage{setspace}
\input{glyphtounicode} % PDF output to ensure proper mapping of glyphs to Unicode characters
% \linespread{0.8}
\setstretch{1}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue
}

% fancy
\pagestyle{fancy}
\fancyhf{} % clear header and footer fields
\fancyfoot{}
\setlength{\footskip}{1cm}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
% \addtolength{\textheight}{0in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sections formatting
\titleformat{\section}{
	\scshape
	\raggedright
	\large
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

% generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ==============================

% custom commands
\titlespacing{\section}{0pt}{11pt}{15pt}

\newcommand{\resumeItem}[1]{
  	\item{
    	{#1}
  	}
}

\newcommand{\resumeItemThin}[1]{
  	\item{
    	{#1 \vspace{-3pt}}
  	}
}

\newcommand{\resumeSubHeading}[4]{
  \item
    \begin{minipage}[t]{0.985\textwidth}
      	\textbf{#1} \hfill #2 \\[1pt]
      	\textit{#3} \hfill \textit{#4}
    \end{minipage}
	\vspace{-3pt}
}

\newcommand{\resumeExperienceHeading}[4]{
  \item
    \begin{minipage}[t]{0.985\textwidth}
      	\textbf{#1} \hfill #2 \\[1pt]
      	\textit{#3} \hfill \textit{#4}
    \end{minipage}
	\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{minipage}[t]{0.985\textwidth}
      	\textbf{#1} \hfill \\[1pt]
      	\textit{#2}
    \end{minipage}
	\vspace{-2pt}
}

\newcommand{\resumeSkillsHeading}[0]{
	\item
}

% \newcommand{\resumeSubItem}[1]{
% 	\resumeItem{#1}
% 	\vspace{-4pt}
% }

\renewcommand\labelitemii{
	$\vcenter{
		\hbox{\tiny$\bullet$}
	}$
}

\newcommand{\resumeSubHeadingListStart}{
  	\begin{itemize}[leftmargin=0.00in, rightmargin=-0.2in, label={}]
  	\vspace{3pt}
}

\newcommand{\resumeSubHeadingListEnd}{
  	\end{itemize}
	\vspace{-10pt}
}
\newcommand{\resumeItemListStart}{
  	% \vspace{3pt}
	\begin{itemize}[leftmargin=0.15in, rightmargin=0.15in]
}

\newcommand{\resumeItemListEnd}{
  	\end{itemize}
	\vspace{-5pt}
}

% ==============================

\begin{document}

\begin{center}
	\textbf{\Huge \scshape {Juhun Park}} \\ 
	\vspace{3pt}
	% No sponsorship needed, F1 OPT \\
	 202-924-4546 $|$
	\href{mailto:juhunpark32@gmail.com}{juhunpark32@gmail.com} $|$
	\href{https://www.juhunpark.me/}{juhunpark.me} $|$
	\href{https://linkedin.com/in/juhun-park}{linkedin.com/in/juhun-park} $|$
	\href{https://github.com/juhun32}{github.com/juhun32}
\end{center}

% Education
\section{Education}
\resumeSubHeadingListStart

\resumeSubHeading
	{George Mason University}{Expected May 2027}
	{Bachelor of Science in Computer Science}{GPA: 4.0}
	\resumeItemListStart
		\resumeItemThin{\textbf{Relevant Coursework: } Data Structures, Low-level Programming, Computer Systems and Programming}
		\resumeItemThin{\textbf{Honors: }{\$20,000 Merit Scholarship Recipient}}
		\resumeItemThin{\textbf{Teaching Assistant: } CS 310 -- Data Structures}
	\resumeItemListEnd

\resumeSubHeadingListEnd

% Work experience
\section{Experience}
\resumeSubHeadingListStart

\resumeExperienceHeading
	{Google Developer Groups} {Aug 2025 -- Present}
	{Lead Developer, George Mason University} {Fairfax, VA}
	\resumeItemListStart
		\resumeItem{Architected a course scheduler with Go and PostgreSQL to ingest and manage 10,000+ university course sections.}
		\resumeItem{Integrated backtracking algorithm to solve the constraint satisfaction problem, generating conflict-free timetables.}
		\resumeItem{Engineered a data pipeline using Python and GitHub Actions to automatically scrape course catalog with 99.9\% accuracy.}
		\resumeItem{Scaled with RabbitMQ and Redis for asynchronous processing, supporting 100+ concurrent users without degradation.}
	\resumeItemListEnd

\resumeExperienceHeading
	{Northwestern University} {Jun 2025 -- Aug 2025}
	{Software Engineer Intern} {Evanston, IL}
	\resumeItemListStart
		\resumeItem{Built an alumni networking platform with SvelteKit and ASP.NET, serving 150 users with 99.9\% uptime on Cloudflare.}
		\resumeItem{Designed a PostgreSQL schema, optimized indexes, SQL functions on Supabase achieving p99 sub-5ms query latency.}
		\resumeItem{Configured a multi-tier caching strategy using Cloudflare CDN and a Redis cache, offloading 95\% of read requests.}
	\resumeItemListEnd

\resumeSubHeadingListEnd

% Projects
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
	{Revive.fyi: Tech Career Platform \textnormal{$|$ \href{https://github.com/juhun32/copium}{GitHub} $|$ \href{https://www.copium.dev}{copium.dev}}}
	{{Go, TypeScript, SvelteKit, PostgreSQL, Algolia, GCP, AWS, Cloudflare}}
	\resumeItemListStart
		\resumeItem{Launched an internship management platform with SvelteKit and PostgreSQL, processing 2000+ weekly applications.}
		% \resumeItem{Scaled real-time analytics pipeline to 1k+ events/s with Kafka and Go consumers on AWS ECS, feeding into ClickHouse.}
		\resumeItem{Delivered an 80\% reduction in query latency for BigQuery analytics by leveraging CQRS architecture.}
		\resumeItem{Migrated media storage to Cloudflare R2, architecting a zero-egress pipeline without incurring AWS data transfer fees.}
		\resumeItem{Implemented fault-tolerant compensating transactions for consistency across 3 data stores with automated retries.}
	\resumeItemListEnd

\resumeProjectHeading
	{Castle Postdate: Cycle Scheduler \textnormal{$|$ \href{https://github.com/juhun32/calple}{GitHub} $|$ \href{https://www.calple.date}{calple.date}}}
	{{Go, Next.js, Firestore, Docker, GCP Cloud Run}}
	\resumeItemListStart
		\resumeItem{Deployed an event pipeline using GCP Pub/Sub to ingest disparate streams into a unified Firestore state model.}
		\resumeItem{Developed a Go microservice to consume event streams, merging data real-time to predict and identify schedule conflicts.}
		\resumeItem{Achieved sub-100ms event synchronization latency by optimizing Firestore listener patterns \& gRPC communication.}
	\resumeItemListEnd

\resumeProjectHeading
    {\textbf{Sequantial: Telemetry Analytics} \textnormal{$|$ \href{https://github.com/juhun32/project-verstappen}{GitHub}}}
    {{Go, WebSockets, Docker, OCI (ARM64), Windows API (Shared Memory)}}
    \resumeItemListStart
        \resumeItem{Engineered a high-performance telemetry pipeline in Go to ingest real-time physics data via zero-copy shared memory.}
        \resumeItem{Architected a concurrent distribution system with WebSockets \& Go routines, achieving sub-10ms states synchronization.}
        \resumeItem{Optimized network efficiency with client-side batching and data aggregation, maintaining zero operational costs.}
	\resumeItemListEnd

\resumeSubHeadingListEnd

% -----------TECHNICAL SKILLS-----------

\section{Technical Skills}

\resumeSubHeadingListStart

\resumeSkillsHeading

\resumeItemListStart
\resumeItemThin{\textbf{Languages: }{Python, TypeScript, JavaScript, Go, Java, SQL, C, C\#}}
% \resumeItemThin{\textbf{Libraries \& Frameworks: }{React, SvelteKit, FastAPI, Django, Flask, .NET, PostgreSQL, Pytest}}
% \resumeItemThin{\textbf{Web \& APIs: } HTTP, HTML/DOM, CSS, AJAX, REST APIs, JSON, OAuth/OIDC}
\resumeItemThin{\textbf{Frameworks: }{React, Node.js, Django, Flask, Next.js, SvelteKit, FastAPI, .NET, PostgreSQL}}
\resumeItemThin{\textbf{Tools \& Platforms: }{Git, GCP, Vercel, Cloudflare, Pub/Sub, AWS, Linux, RabbitMQ, Docker, Redis, Kafka}}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}